---
name: Monica
surname: Moisa
position: "Market Research Consultant - Apparel Industry"
phone: +1 (408) 310-3061
www: modemoconsulting.com
email: "monicaamoisa@egmailcom"
github: https://github.com/monicamoisa/quarto_website.git
linkedin: https://linkedin.com/in/monica-moisa-ba6387172
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::latexcv:
    theme: classic
header-includes:
   - \usepackage{enumitem}
   - \setlist[itemize]{nosep, left=0pt}
   - \setlist[enumerate]{nosep, left=0pt}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

if (!requireNamespace(c("tinytex","vitae","tibble"), quietly = TRUE)) {
  install.packages(c("tinytex","vitae","tibble"))
}

if (Sys.which("pdflatex") == "" && !tinytex::is_tinytex()) {                    
  message("► TinyTeX not found – installing")
  tinytex::install_tinytex()        
} else {
  message("✓ LaTeX present – no installation needed.")
}

library(vitae)
library(tibble)
```

# Professional Summary

Market research consultant at the forefront of AI integration in the apparel sector, I bring a distinctive blend of industry expertise and technological innovation to businesses seeking competitive advantage in today's rapidly evolving market.

# Technical Skills

-   **Programming Languages:** R, SQL
-   **Web Technologies:** HTML, CSS/SCSS, Quarto, CMS Platforms, Analytics Tools
-   **Product Development and Design Software:** PLM, Clo3D

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ College, ~ Institution,
  "MSDM", "2023– Expected Graduation 2025", "Singelyn Graduate School of Business - Digital Marketing", "California State Polytechnic University, Pomona",
  "BS", "1990 – 1996", "School of Textile Engineering", "Gh. Asachi Polytechnical University, Iasi"
)

```

```{r}
tribble(
  ~ Years, ~ Company, ~ Duties, ~ Title,

  "2023 – present", "Ariat International",
  list(
    "Supported small businesses in creating the infrastructure needed for healthy growth.",
    "Built partnerships with Sourcing, Product Development, Design, Merchandising teams.",
    "Pioneered Clo3D integration."
  ),
  "Sr. Technical Designer",

  "2018– 2023", "Modemo Consulting",
  list(
    "Supported small businesses in creating the infrastructure needed for healthy growth.",
    "Built partnerships with Sourcing, Product Development, Design, Merchandising teams.",
    "Pioneered Clo3D integration."
  ),
  "Apparel Consultant" ,

  "2010– 2018", "Patrol Sunguard",
  list(
    "Managed responsibilities of product creation, marketing strategy, web design.",
    "Explored target demographics, executed competitor research."
  ),
  "Entrepreneur"  )

```
